MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Now, each community tries to find the closest community within the trained $CFVS$ set. Following its decision profile, the community can have a good estimate of possible strategic decisions it can adopt. Basically the trained profiles benefit the new web services in two ways. First they provide the communities with a set of viable communities to join with. And an estimation of utility which the community would gain in long term based on each available decision. In this experiment, we let communities follow the best decision within the decision tree provided to the them.

@@

In order to evaluate the performance of the mechanism we have used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategy correctly, for each community we evaluated the training process by replacing the community in set with the closest one, which it gets the strategy profile from. If actions are same and same utility levels are gained, we classify the decision as correct, otherwise its a wrong decision. The area under the \emph{ROC curve} called \emph{AUC} is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one\cite{xxx} and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of MLISA decision making mechanism. We compare our method with two other methods. The rational is based on assumption that communities as rational agents would join a community that increases their utilities. And the greedy method only looks up the available list of communities and joins the one that maximizes its utility without considering any long term strategy or the other communities acceptance scenario. Figure \ref{roc5} compares the results for all these methods. The two other methods have very high failure rate compared to our method. Table \ref{fail_rate} illustrates the number of communities which failed to find the optimal and best collaboration group. The results prove the need of a long term training model for successful decision making process.

>>>>

Now, each community tries to find the closest community within the trained $CFVS$ set. Following its decision profile, the community can get a good estimate of the possible strategic decisions it can adopt. Basically, the trained profiles benefit the new web services in two ways. First, they provide the communities with a set of viable communities to join. Second, they provide an estimation of long-term utility gain for each available decision. In this experiment, we let communities follow the best decision within the decision tree provided to the them.

@@

In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile. If the actions are the same and the same utility levels are gained, we classify the decision as correct. Otherwise, it is classified as a wrong decision. \emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one\cite{xxx}, and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the MLISA decision making mechanism. We compare our method with two other methods. The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility. And the \emph{greedy} method only looks up the available list of communities and joins the one that maximizes its utility without considering any long term strategy or the other communities acceptance scenario. Figure \ref{roc5} compares the results for all these methods. The two other methods have very high failure rate compared to our method. Table \ref{fail_rate} illustrates the number of communities which failed to find the optimal and best collaboration group. The results prove the need of a long term training model for successful decision making process.
